---
title: "EDA - Casino Data"
author: "Aakanksha Baid"
date: "1/27/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1a: Import the data 

```{r}
# import
casino_DF <- read.csv("Data/casino.csv")
```

## Step 1b: Install the package tidyverse 

```{r}
#install.packages("tidyverse")
library(tidyverse)
```


## Step 2: Scatter plot 1

```{r}
# hold vs coin_in colored by location
ggplot(data=casino_DF) +
  geom_point(mapping = aes(x=hold,y=coin_in,color=location))
```

The above plot shows a negative relationship between hold and coin-ins.


## Step 3: Scatter plot 2

```{r}
# hold vs coin_in for each location
ggplot(data=casino_DF) +
  geom_point(mapping = aes(x=hold,y=coin_in)) +
  facet_wrap(~ location,nrow = 5)
```

The above plot shows that the relationship between hold and coin-in is in fact not negatively related for all locations, when we factor in location.


## Step 4: Interpret the plots

a. The relationship between holds and coin-in of slot machines varies across locations as location A has high coin-in even at low hold which is also the case for locations I and J, whereas for other locations, hold is fairly constant at low coin-ins. This is not clear from Step 2 plot.

b. The Step 3 plot is better to interpret relationships between the variables as it clearly displays the relationship between coin-in and hold for each location and the graph is intuitive. The step 2 plot is not visually appealing as it is not able to display the large number of locations on the same plot (eg. location A is missing) making it difficult to identify any meaningful relationship due to high number of locations. 